\sysfull

### 2018-04-15 paper/intro.tex

In this work, we introduce a new system called \sys, which executes a task-based
intermittent program by dynamically coalescing its tasks.
\sys accepts any static decomposition (i.e., from the programmer or from a compiler) 
and coalesces its tasks at runtime. Two consecutive, coalesced tasks execute  
with no commit or task transition overhead between them, instead performing
task-end commit actions at the end second task only.
%
When there is sufficient energy to execute both tasks, two distinct, small
tasks are effectively executed as a single large task, preserving the atomicity
of both.  If power fails during a coalesced task, execution restarts from the
{\em first} of the coalesced tasks.  Figure~\ref{fig:coalesce} (bottom)
illustrates how dynamic coalescing changes the earlier execution and highlights
the change in memory model necessary to not break atomicity.

@@

%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.

While a compiler can use static data privatization and commit instrumentation
(i.e., redo-logging) to eliminate statically identifiable, inter-task data
dependences~\citep{alpaca}, a \emph{dynamic} dependence between two coalesced
tasks requires dynamic privatization and commit actions. 
%
To ensure consistency and respect inter-task dependences, \sys uses a novel
approach to \emph{memory virtualization} that buffers non-volatile variable
updates in volatile memory during coalesced task execution, before committing
them to non-volatile memory at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.

A static task decomposition model assumes that each
single task can execute to completion.  If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. To avoid non-termination under adversarial 
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial commit avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted.  Partial commit violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial commit
instead risking non-termination.

>>>>

This paper introduces a new system called \sys, which executes a task-based
intermittent program by dynamically coalescing/splitting its tasks.
\sys accepts any static decomposition (i.e., from the programmer or from a compiler) 
and coalesces/splits its tasks at runtime. Two consecutive, coalesced tasks execute  
with no commit or task transition overhead between them, instead performing
task-end commit actions at the end second task only.
%
When there is sufficient energy to execute both tasks, two distinct, small
tasks are effectively executed as a single large task, preserving the atomicity
of both.  If power fails during a coalesced task, execution restarts from the
{\em first} of the coalesced tasks.  Figure~\ref{fig:coalesce} (top)
illustrates how dynamic coalescing changes the earlier execution and highlights
the change in memory model necessary to not break atomicity. On the other hand, a large task that requires more energy to complete than a device's fixed energy buffer is split by \sys to enable task termination, as depicted in Figure~\ref{fig:coalesce} (bottom).

@@

%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
\textbf{Challenges.} While a compiler can use static data privatization and commit instrumentation
(i.e., redo-logging) to eliminate statically identifiable, inter-task data
dependences~\citep{alpaca}, a \emph{dynamic} dependence between two coalesced
tasks requires dynamic privatization and commit actions. 
%
To ensure consistency and respect inter-task dependences, \sys uses a novel
approach to \emph{memory virtualization} that buffers non-volatile variable
updates in volatile memory during coalesced task execution, before committing
them to non-volatile memory at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.
A static task decomposition model assumes that each
single task can execute to completion.  If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. To avoid non-termination under adversarial 
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial commit avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted.  Partial commit violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial commit
instead risking non-termination.
